Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-05-14 ltx/data_paper/DataPaper.tex
minor edits

$\Xi_3, \Xi_5$&$O(Tn_x^2n_{\theta})$&$O(Tn_x^2n_r^2)+O(Tn_xn_{\theta}n_r^2)$ \\
$\Xi_4$&$O(Tn_x^2n_{\theta})+O(Tn_xn_{\theta}^2)$&$O(Tn_x^4n_{\theta}n_r^2)+O(Tn_x^3n_{\theta}^2n_r^2)$\\

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelBasis1.pdf}
\end{center}
\caption{{\bf Connectivity kernel support approximation.} The approximate support of the kernel is shown by the red circle. Black area shows the non-zero values of the support after thresholding. A $5\times5$ grid of basis functions (blue circles) used to reconstruct the connectivity kernel.}
\label{fig:KernelWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
\end{center}
\caption{{\bf Disturbance support approximation}. }
\label{fig:DisturbanceWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimate.pdf}
\end{center}
\caption{{\bf Connectivity kernel estimates.} (A) Actual kernel. (B) The mean kernel estimate over 100 realisations}
\label{fig:KernelEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
\end{center}
\caption{{\bf Cross-sections of connectivity kernel estimates.} Actual kernel and the mean kernel estimates are shown with blue and green lines respectively. Each of the estimate from Monte Carlo simulation is shown with black line. The 95\% confidence intervals are shown by shaded red area.}
\label{fig:KernelEstimateCrossSection}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Histogram.pdf}
\end{center}
\caption{{\bf Histograms of the parameter estimates over 100 realizations}. The actual and mean of the estimated parameter values are shown by solid and dotted lines respectively. (A) The histogram of the synaptic dynamic parameter, $\xi$. (B) The histogram of the observation noise variance, $\sigma_{\epsilon}$. (C) The histogram of the disturbance noise variance, $\sigma_d^2$}.
\label{fig:Histogram}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics[scale=1]{./Figures/FieldEstimates.pdf}
\end{center}
\caption{{\bf Neural field estimates at different time instants}. In each subplot, true (gray line) and reconstructed neural field (red dots) are plotted versus spatial index.}
\label{fig:FieldEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Q.pdf}
\end{center}
\caption{{\bf Lower-bound of the log-likelihood}. $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$.}
\label{fig:LowerBound}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

>>>>

$\Xi_3, \Xi_5$&$O(Tn_x^2n_{\theta})$&$O(Tn_x^3)+O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)$ \\
$\Xi_4$&$O(Tn_x^2n_{\theta})+O(Tn_xn_{\theta}^2)$&$O(Tn_x^4n_{\theta})+O(Tn_x^3n_{\theta}^2)+O(Tn_xn_{\theta}n_r)$\\

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelBasis1.pdf}
\end{center}
\caption{{\bf Connectivity kernel support approximation.} The approximate support of the kernel is shown by the red circle. Black area shows the non-zero values of the support after thresholding. A $5\times5$ grid of basis functions (blue circles) used to reconstruct the connectivity kernel.}
\label{fig:KernelWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
\end{center}
\caption{{\bf Disturbance support approximation}. }
\label{fig:DisturbanceWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimate.pdf}
\end{center}
\caption{{\bf Connectivity kernel estimates.} (A) Actual kernel. (B) The mean kernel estimate over 100 realisations.}
\label{fig:KernelEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
\end{center}
\caption{{\bf Cross-sections of connectivity kernel estimates.} Actual kernel and the mean kernel estimates are shown with blue and green lines respectively. Each of the estimate from Monte Carlo simulation is shown with black line. The 95\% confidence intervals are shown by shaded red area.}
\label{fig:KernelEstimateCrossSection}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Histogram.pdf}
\end{center}
\caption{{\bf Histograms of the parameter estimates over 100 realizations}. The actual and mean of the estimated parameter values are shown by solid and dotted lines respectively. (A) The histogram of the synaptic dynamic parameter, $\xi$. (B) The histogram of the observation noise variance, $\sigma_{\epsilon}$. (C) The histogram of the disturbance noise variance, $\sigma_d^2$.}
\label{fig:Histogram}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics[scale=1]{./Figures/FieldEstimates.pdf}
\end{center}
\caption{{\bf Neural field estimates at different time instants}. In each subplot, true (gray line) and reconstructed neural field (red dots) are plotted versus spatial index.}
\label{fig:FieldEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Q.pdf}
\end{center}
\caption{{\bf Convergence of the EM algorithm.} The mean of the lower bound of the log-likelihood function over 100 realisations. The change in lower bound drops below 0.009 percent after 15 iterations}
%  $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$
\label{fig:LowerBound}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
